Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/analysis.tex
small fixes

The number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure\ \ref{fig:ntypes}\ (right).
%Here, we observe that the 
The rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10\ or even 20\ different name types, even after applying the frequency thresholds. This clearly indicates that different instances annotated with the same 
%name and 
%\cs{(removed "name and") 
%The synsets could have different names -- maybe say "or even same name"?}
synset in \vg trigger different naming variants (also see examples in Figure \ref{fig:ex-high-low-agreement}). 
Implications of this will be discussed below in Section \ref{subsec:discuss}.

@@

%As type counts give a rather rough indication for variation in object naming, 
Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
\begin{itemize}
\setlength{\itemsep}{2pt}
\setlength{\parskip}{1pt}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. \item \textbf{N}: the average number of types in the response set of ManyNames.
\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name.
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
\end{itemize}

@@

It would be desirable to explicitly assess models towards their ability to account for naming variants of an instance (e.g.,~in how far are the top N predicted names valid alternatives, such as, dog, animal, pet vs. dog, animal, hat). 

@@

as we outlined in Section\ \ref{sec:relwork}, previous work has focused on the determination of canonical names, or on "granularity-aware" models, where naming variants are hierachically related. 

@@

For the same reason, even fine-grained recognition models (as those trained on ILSVRC \cite{ILSVRC15}) cannot be expected to be able to simply infer the recognition of more general classes.

>>>>

The number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure\ \ref{fig:ntypes}\ (right).
%Here, we observe that the 
The rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10\ or even 20\ different name types, even after applying the frequency thresholds. This clearly indicates that different instances annotated with the same 
%name and 
%\cs{(removed "name and") 
%The synsets could have different names -- maybe say "or even same name"?}
synset in \vg trigger different naming variants (also see examples in Figure \ref{fig:ex-high-low-agreement}). 
Implications of this will be discussed in Section \ref{subsec:discuss}.

@@

%As type counts give a rather rough indication for variation in object naming, 
Next, we look at the following agreement measures, computed with $t>1$: 
%$t=1$: % to assess agreement on the object names:
\begin{itemize}
% \setlength{\itemsep}{2pt}
% \setlength{\parskip}{1pt}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. \item \textbf{N}: the average number of types in the response set of ManyNames.
\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name.
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
\end{itemize}

@@

It would be desirable to explicitly assess models towards their ability to account for naming variants of an instance (e.g.,~in how far are the top N predicted names valid alternatives, such as, \textsl{dog, animal, pet} vs. \textsl{dog, animal, hat}). 

@@

as we outlined in Section\ \ref{sec:relwork}, previous work has focused on the determination of canonical names, or on "granularity-aware" models, where naming variants are hierarchically related. 

@@

For the same reason, even fine-grained recognition models (as those trained on ILSVRC) cannot be expected to be able to simply infer the recognition of more general classes.

### 2019-05-21 papers/EMNLP2019/data-collection.tex
small fixes

We take data from \vg~\cite{krishna2016visualgenome}, which
% aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
contains a dense region-based labeling of $108k$~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs, 
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
%As common in Computer Vision, O
Objects are localized as 
%identified via
 bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

\subsection{Elicitation Procedure}
\label{ssec:elicitation}
To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
In initial pilot studies, we found object identification via bounding boxes to be problematic.
In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear. 
%The Appendix~\ref{app:instructions} contains the task instructions and details about the pruning and data procedure.
We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images. 
(We refer to the Supplemental Material for the task instructions and more details on the pruning and the dataset.) 
We then did 3 more collection rounds, and shuffled the set of images per task between each round. 
Workers could only participate in one round, to avoid workers annotating an instance more than once. 
We obtained a total of 36 names per image (i.e.,\ objects).
As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in L\&V (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
%\cs{Maybe say something about the rejections, if space permits it.}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

We take data from \vg~\cite{krishna2016visualgenome}, which
% aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
contains a dense region-based labeling of $108$K~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs, 
all linked to WordNet synsets \cite{fellbaum1998wordnet}.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
%As common in Computer Vision, O
Objects are localized as 
%identified via
 bounding boxes, as in Figure~\ref{fig:cake}.% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

\subsection{Elicitation Procedure}
\label{ssec:elicitation}
To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
In initial pilot studies, we found object identification via bounding boxes to be problematic.
In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear. 
%The Appendix~\ref{app:instructions} contains the task instructions and details about the pruning and data procedure.
We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images. 
(We refer to the Supplemental Material for the task instructions and more details on the pruning and the dataset.) 
We then did 3 more collection rounds, and shuffled the set of images per task between each round. 
Workers could only participate in one round, to avoid workers annotating an instance more than once. 
We obtained a total of 36 names per image (i.e.,\ object).
As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in L\&V (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
%\cs{Maybe say something about the rejections, if space permits it.}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2019-05-21 papers/EMNLP2019/modeling.tex
small fixes

%\paragraph{Data}
Bottom-up was trained on a $1,600$\ object names, manually curated by the authors. % (the authors manually removed names with poor a detection performance from the original set). 
They did not merge semantically similar classes, such as \textsl{person} and \textsl{guy}, which is in line with the data structure of MN. %\gbt{Carina, I don't understand the following sentence}
%
From this set, we test on $1,254$~names (we removed the $346$\ names which are not in MN), and on $24,585$~images from MN, after filtering those whose \vg name was not in the vocabulary. 
Note that $22,304$~of the images were also part of Bottom-up's training data; below we report separate results for data in and out of the training set. 
%
%(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
% Despite the much larger vocabulary of MN ($XX$\ name types), $346$~types are not in MN, which we removed, resulting in a final vocabulary (\mbox{MN$\cap$VG}) of 
% Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data). 
\paragraph{Evaluation Procedure}
We apply Bottom-up to each image and extract the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.\footnote{We converted the scores to our vocabulary size.}

Model effectiveness is assessed in two settings, the commonly used single-label setting and a multi-label setting. 
In the former, for each instance, we compare the model's top prediction (the object label with the highest score in\ $S$) to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN}, respectively).
In the multi-label setting, we report the average accuracy of the top prediction matching any of the responses in MN.
We also test the model's ability to mimic the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts). 
%; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}). 
We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD? MF name baseline: I would say it's not relevant for this paper (we mainly compare different settings).}.
\gbt{Random baseline values missing; I'm not sure if it makes sense; we could maybe compare it to the single-label distribution: Compare $S$ to $M$, like we do, and then to a distribution to vectors with 1, 0, 0, 0... with MN top. Not sure if this is too ``cheap'' -- is it a matter of course that it will be lower? Not if the distribution doesn't reflect the actual $M$?}

\iffalse
\textsl{top}: the model's top prediction
\begin{itemize}
	\item \textbf{=VG} The average model accuracy of \textsl{top} on the VG names
	\item \textbf{=MN} The average model accuracy of \textsl{top} on the top response in ManyNames
	\item \textbf{$\in$MN} The average model accuracy of \textsl{top} to match any name of the responses in ManyNames
	\item \textbf{KL} The average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ of the model's softmax output~$S$ and the  probability distribution~$M$ over ManyNames, estimated by normalizing the name counts per instance
\end{itemize}
\fi

%\subsection{Results \& Discussion}
\paragraph{Results and Discussion}
Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
%\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material. All important points can be made at that level, and this way we gain space.}\sz{I would not do that}
% Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
% The latter two sets are disjoint. 
Strikingly, the model performs worse on \vg than on the top MN response, even though the model was trained on \vg names and saw the majority of the instances during training: It has a general accuracy of $76.8$\ on MN, $68.7$\ on \vg (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger,\ $52.6$ vs.\ $20.7$.
We hypothesize two main reasons for this difference.
First, the top MN name may be more reliable because it is collected from multiple workers: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textsl{sandwich}, but \textsl{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three workers still chose \textsl{sandwich}).
Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.
% It achieves a higher accuracy of up to\ 55\% points on instances for which MN and the VG name differ (\textsc{buildings}, VG$\neq$MN). 
% The reasons may be that MN is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).

Results in the multi-label setting, $\in$MN, suggest that the current single-label evaluation dominant in the field may be too stringent: In \mbox{$92-95\%$}\ of the cases across conditions, the model's top choice corresponds to a name actually produced by human subjects for that object--even in the unseen images (\mbox{$\neg$\textit{Training}}).
This is a very high result.
% In the multi-label setting, $\in$MN, the difference in accuracy between the objects in the \textit{All} and in the subset VG$\neq$MN is much lower compared to the single-label setting ($-2.5$\% vs.\ $-24.2$\%\ points, all domains). 
%Comparison to the results on unseen images demonstrates Bottom-up's generalization ability. 
% While the difference varies highly across the domains (All vs. \mbox{$\neg$\textit{Training}}), it is negligible on average (row \textit{all}), and the same on the \mbox{VG$\neq$MN} images. 
Taken together, the results suggest that our ManyNames dataset provides a more robust evaluation framework than single-label datasets, allowing researchers to better differentiate between possible alternative names and true mistakes.

The dataset furthermore allows for comparing models on weighted naming alternatives, as illustrated by measuring the KL divergence. 
As shown in the table, the model outperforms the random baseline on all image sets. \cs{we could also (better?) use the average responses over all instances in MN -- TBD}
\gbt{The following is interesting but I would move it to supp. material (see above).}
It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}.
%, which might \sz{?} contain occluded or unclear bounding boxes.% \cs{can we say that?}. 
%For these more difficult instances (VG$\neq$MN),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain

Qualitative analysis suggests that Bottom-up presents many of the phenomena related to naming variation that we find in humans.
In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{boy-helmet},\ Fig.\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror cases of human ``referential uncertainty'' 
(\textsl{man-shirt}, \textsl{bed-sheet}).
We also find cross-classification (\textsl{boy-batter}) and metonymy (\textsl{food-plate}). 
Finally, it reflects perceptual mistakes caused by unclear images (\textsl{street-bridge}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{bridge-sky}, \textsl{player-dirt}. 
%
\iffalse
\begin{itemize}
	\item VG worse than MN; considering that model was trained on VG - is it because MN has easier labels? Does this mean that generalisation ability is better evaluated on MN?
	\item VG$\neq$MN much worse than All $\Rightarrow$ Former has more difficult/ambiguous images (for both? classifier and human?)
	\item for those more difficult images (VG$\neq$MN), the difference for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
	\item accuracy drops for notTrain (except for vehicles MN), but is still much better than VG$\neq$MN  
\end{itemize}

>>>>

%\paragraph{Data}
Bottom-up was trained on a set of $1,600$\ object names, manually curated by the authors. % (the authors manually removed names with poor a detection performance from the original set). 
They did not merge semantically similar classes, such as \textsl{person} and \textsl{guy}, which is in line with the data structure of MN. %\gbt{Carina, I don't understand the following sentence}
%
From this set, we test on $1,254$~names (we removed the $346$\ names which are not in MN), and on $24,585$~images from MN, after filtering those whose \vg name was not in the vocabulary. 
Note that $22,304$~of the images were also part of Bottom-up's training data; we report separate results for data in and out of the training set. 
%
%(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
% Despite the much larger vocabulary of MN ($XX$\ name types), $346$~types are not in MN, which we removed, resulting in a final vocabulary (\mbox{MN$\cap$VG}) of 
% Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data). 
\paragraph{Evaluation Procedure}
We apply Bottom-up to each image and extract the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.\footnote{We converted the scores to our vocabulary size.}

Model effectiveness is assessed in two settings, the commonly used single-label setting and a multi-label setting. 
In the former, for each instance, we compare the model's top prediction (the object label with the highest score in\ $S$) to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN}, respectively).
In the multi-label setting, we report the average accuracy of the top prediction matching any of the responses in MN.
We also test the model's ability to mimic the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts). 
%; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}). 
We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline. 
% \cs{not sure whether the latter, at least in its current form, makes sense. TBD? MF name baseline: I would say it's not relevant for this paper (we mainly compare different settings).}. 
%
\iffalse
\textsl{top}: the model's top prediction
\begin{itemize}
	\item \textbf{=VG} The average model accuracy of \textsl{top} on the VG names
	\item \textbf{=MN} The average model accuracy of \textsl{top} on the top response in ManyNames
	\item \textbf{$\in$MN} The average model accuracy of \textsl{top} to match any name of the responses in ManyNames
	\item \textbf{KL} The average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ of the model's softmax output~$S$ and the  probability distribution~$M$ over ManyNames, estimated by normalizing the name counts per instance
\end{itemize}
\fi

%\subsection{Results \& Discussion}
\paragraph{Results and Discussion}
Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
%\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material. All important points can be made at that level, and this way we gain space.}\sz{I would not do that}
% Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
% The latter two sets are disjoint. 
Strikingly, the model performs worse on \vg than on the top MN response, even though the model was trained on \vg names and saw the majority of the instances during training: It has a general accuracy of $76.8$\ on MN, $68.7$\ on \vg (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger,\ $52.6$ vs.\ $20.7$.
We hypothesize two main reasons for this difference.
First, the top MN name may be more reliable because it is collected from multiple workers: For instance, in the fourth example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textsl{sandwich}, but \textsl{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three workers still chose \textsl{sandwich}).
Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.
% It achieves a higher accuracy of up to\ 55\% points on instances for which MN and the VG name differ (\textsc{buildings}, VG$\neq$MN). 
% The reasons may be that MN is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).

Results in the multi-label setting, $\in$MN, suggest that the current single-label evaluation dominant in the field may be too stringent: In \mbox{$92-95\%$}\ of the cases across conditions, the model's top choice corresponds to a name actually produced by human subjects for that object---even in the unseen images (\mbox{$\neg$\textit{Training}}).
This is a very high result.
% In the multi-label setting, $\in$MN, the difference in accuracy between the objects in the \textit{All} and in the subset VG$\neq$MN is much lower compared to the single-label setting ($-2.5$\% vs.\ $-24.2$\%\ points, all domains). 
%Comparison to the results on unseen images demonstrates Bottom-up's generalization ability. 
% While the difference varies highly across the domains (All vs. \mbox{$\neg$\textit{Training}}), it is negligible on average (row \textit{all}), and the same on the \mbox{VG$\neq$MN} images. 
Taken together, the results suggest that our ManyNames dataset provides a more robust evaluation framework than single-label datasets, allowing researchers to better differentiate between possible alternative names and true mistakes.

The dataset furthermore allows for comparing models on weighted naming alternatives, as illustrated by measuring the KL divergence. 
As shown in the table, the model outperforms the random baseline on all image sets (with a KL between \mbox{$6.5$ and $6.9\%$}, see caption). 
%\cs{we could also (better?) use the average responses over all instances in MN -- TBD} 
%\gbt{The following is interesting but I would move it to supp. material (see above).}
It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Table\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}. %, which tend to contain occluded or unclear bounding boxes. 
%, which might \sz{?} contain occluded or unclear bounding boxes.% \cs{can we say that?}. 
%For these more difficult instances (VG$\neq$MN),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain

Qualitative analysis suggests that Bottom-up presents many of the phenomena related to naming variation that we find in humans.
In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{boy-helmet},\ Figure\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror cases of human ``referential uncertainty'' 
(\textsl{man-shirt}, \textsl{bed-sheet}).
We also find cross-classification (\textsl{boy-batter}) and metonymy (\textsl{food-plate}). 
Finally, it reflects perceptual mistakes caused by unclear images (\textsl{street-bridge}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{bridge-sky}, \textsl{player-dirt}. 
%
\iffalse
\begin{itemize}
	\item VG worse than MN; considering that model was trained on VG - is it because MN has easier labels? Does this mean that generalisation ability is better evaluated on MN?
	\item VG$\neq$MN much worse than All $\Rightarrow$ Former has more difficult/ambiguous images (for both? classifier and human?)
	\item for those more difficult images (VG$\neq$MN), the difference for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
	\item accuracy drops for notTrain (except for vehicles MN), but is still much better than VG$\neq$MN  
\end{itemize}

### 2019-05-21 papers/EMNLP2019/relwork.tex
small fixes

\paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, (cf.\ \newcite{regan2000human,rossion2004revisiting}). 
An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure\ \ref{fig:cake}.
Subjects reach very high agreement in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
Recognition of instances (as opposed to categories) in images has also been the focus of Computer Vision, where state-of-the-art systems are now able to predict thousands of different categories, (e.g.\ \newcite{googlenet}). 
Current recognition benchmarks use labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically implement a single ground-truth label approach. 
%, but typically implement multi-label classifiers where relations between labels are not considered \cite{ILSVRC15}. 
%\cs{do you mean multi-label classifiers in single ground-truth label settings?}
In L\&V, deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly. For instance, many labels in the ILSVRC15 challenge correspond to very specific breeds of animals, whereas other common categories  for,\ e.g.,\ people are missing.

@@

\paragraph{Work on Object Naming} that models which \textit{word} (i.e.\ not label) a speaker will use to name an object is relatively scarce.
Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focused mostly on the selection of attributes % rather than on determining the referent's name 
\cite{krahmer:2012}. 
\newcite{Ordonez:2016} takes up the notion of entry-level categories \cite{rosch1976basic} and transfers an object's predicted fine-grained label to its name using text corpus statistics.
% extend object recognition to naming, taking up the notion of entry-level categories \cite{rosch1976basic}.
%Their model predicts classifies objects into fine-grained categories and then predicts a WordNet synset for retrieving the name, based on frequencies in a text corpus. 
 \newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 
 Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
\cite{rohde2012communicating,graf2016animal}. Our work is a first step towards studying naming in real-world, natural reference.
But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focusses on naming in isolation, rather than reference where naming interacts with attribute selection.

>>>>

\paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, (cf.\ \newcite{regan2000human,rossion2004revisiting}). 
An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure\ \ref{fig:cake}.
Subjects reach very high agreement in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
Recognition of instances (as opposed to categories) in images has also been the focus of Computer Vision, where state-of-the-art systems are now able to predict thousands of different categories, (e.g.\ \newcite{googlenet}). 
Current recognition benchmarks use labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically implement a single ground-truth label approach. 
%, but typically implement multi-label classifiers where relations between labels are not considered \cite{ILSVRC15}. 
%\cs{do you mean multi-label classifiers in single ground-truth label settings?}
In L\&V, deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly. For instance, many labels in the ILSVRC  challenge \cite{ILSVRC15} correspond to very specific breeds of animals, whereas other common categories  for,\ e.g.,\ people are missing.

@@

\paragraph{Work on Object Naming} that models which \textit{word} (i.e.\ not label) a speaker will use to name an object is relatively scarce.
Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focused mostly on the selection of attributes % rather than on determining the referent's name 
\cite{krahmer:2012}. 
\newcite{Ordonez:2016} takes up the notion of entry-level categories \cite{rosch1976basic} and transfers an object's predicted fine-grained label to its name using text corpus statistics.
% extend object recognition to naming, taking up the notion of entry-level categories \cite{rosch1976basic}.
%Their model predicts classifies objects into fine-grained categories and then predicts a WordNet synset for retrieving the name, based on frequencies in a text corpus. 
 \newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 
 Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
\cite{rohde2012communicating,graf2016animal}. Our work is a first step towards studying naming in real-world, natural reference.
But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focuses on naming in isolation, rather than reference where naming interacts with attribute selection.
